---
title: "Practice_1"
author: "Josh Manuel"
date: "2024-06-04"
output : html_document

```{r}
library(tidyr)
library(ggplot2)
library(dplyr)
library(datasets)

#read csv file
data("airquality")
summary(airquality)
head(airquality)
```
Find how many na values in datasets
## 1a. (5%) Are there any missing values in the data? If so, calculate the percentage of missing values present for each feature.

- with colSums function we can determine that the na value in Ozone is 37 and Solar.R is 7.
    Ozone Solar.R    Wind    Temp   Month     Day 
     37       7       0       0       0       0 
     
     
- than create a new variable "missing_percentages" to find percentage of na values/column
  Ozone Solar.R    Wind    Temp   Month     Day 
  24.18    4.58    0.00    0.00    0.00    0.00 
  
  
```{r}
#check na values in each columns
colSums(is.na(airquality))

missing_percentages <- round(colMeans(is.na(airquality))*100, 2)
missing_percentages

```
## 1b.	(8%) Apply the most suitable imputation technique to numerical missing values (from point 2a) and display the imputed data, highlighting changes

columns with na values then get imputated to change the na values to median or mean. then check if function works and update the na values to median/mean.

#check if the missing values is already updated with median value
sum(is.na(airquality))
hasil -> [1] 0

```{r}
#after checking na values, there are a total of 44 na values

missing_ozone <- is.na(airquality$Ozone)
if(any(missing_ozone)){
  airquality$Ozone[missing_ozone] <- median(airquality$Ozone, na.rm = TRUE)
}

missing_Solar <- is.na(airquality$Solar.R)
if(any(missing_Solar)){
  airquality$Solar.R[missing_Solar] <- median(airquality$Solar.R, na.rm = TRUE)
}

#check if the missing values is already updated with median value
sum(is.na(airquality))

```
## 1d. Identify and visualize potential outliers in the data that could significantly influence analysis.
```{r}
airquality %>% 
  ggplot(aes(y = Ozone)) +
  geom_boxplot()


```
